\begin{frame}{Swap-test}

Efficient procedure to calculate the inner product. Since the circuit depth linear in the number of qubits, it can lead to an exponential speed-up (depending on how you encode the data).

\begin{center}
\begin{quantikz}
\lstick{$\ket{0}$}      & \gate{H} & \ctrl{2} & \gate{H} & \meter{} \\
\lstick{$\ket{\psi_1}$} & \qw      & \swap{1} & \qw      & \qw \\
\lstick{$\ket{\psi_2}$} & \qw      & \swap{0} & \qw      & \qw \\
\end{quantikz}
\end{center}

\[p(\text{measure }0) = \frac{1}{2} + \frac{1}{2}|\braket{\psi_1}{\psi_2}|^2\]

\only<2->{\bigskip \emph{Note}: \(\text{distance}(\psi_1, \psi_2)^2 = 2(1-\braket{\psi_1}{\psi_2}) \)}
\end{frame}

\begin{frame}{Swap-test math}
\begin{align*}
    & \ket{0}\ket{\psi_1}\ket{\psi_2} \\
    \to^{(1)}\quad
    & \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})\ket{\psi_1}\ket{\psi_2} \\
    \to^{(2)}\quad & \frac{1}{\sqrt{2}}(\ket{0}\ket{\psi_1}\ket{\psi_2} + \ket{1}\ket{\psi_2}\ket{\psi_1}) \\
    \to^{(3)}\quad & \frac{1}{2}(\ket{0}\ket{\psi_1}\ket{\psi_2} + \ket{1}\ket{\psi_1}\ket{\psi_2} + \ket{0}\ket{\psi_2}\ket{\psi_1} - \ket{1}\ket{\psi_2}\ket{\psi_1}) \\
    = \quad & \frac{1}{2}
\ket{0}(\ket{\psi_1}\ket{\psi_2} + \ket{\psi_2}\ket{\psi_1}) + \frac{1}{2} \ket{1}(\ket{\psi_1}\ket{\psi_2} - \ket{\psi_2}\ket{\psi_1}) 
\end{align*}
\[ p(\text{measure zero}) = \frac{1}{2}(\ket{\psi_1}\ket{\psi_2} + \ket{\psi_2}\ket{\psi_1})^\dagger \frac{1}{2}(\ket{\psi_1}\ket{\psi_2} + \ket{\psi_2}\ket{\psi_1})\]
\end{frame}

\begin{frame}{C-SWAP with multiple qubits per state}
\begin{center}
    \begin{quantikz}
\lstick{$\ket{0}$}      & \gate{H} & \ctrl{2} & \ctrl{3} & \gate{H} & \meter{} \\
\lstick{$\ket{\psi}_0$} & \qw      & \swap{2} & \qw      & \qw      & \qw \\
\lstick{$\ket{\psi}_1$} & \qw      & \qw      & \swap{2} & \qw      & \qw \\
\lstick{$\ket{\phi}_0$} & \qw      & \swap{0} & \qw      & \qw      & \qw \\
\lstick{$\ket{\phi}_1$} & \qw      & \qw      & \swap{0} & \qw      & \qw \\
\end{quantikz}
\end{center}
\end{frame}

\begin{frame}[fragile]{SWAP-test on qiskit}
\begin{minted}{python}
n = 1 # qubit per register
psi = np.array([0, 1])
phi = np.array([1, 0])

qra, qr1, qr2 = QuantumRegister(1), QuantumRegister(n), QuantumRegister(n)
cr = ClassicalRegister(1)
qc = QuantumCircuit(qa, qr1, qr2, cr)
qc.h(qa[0])
qc.initialize(psi, qr1[:])
qc.initialize(phi, qr2[:])
for i in range(n):
    qc.cswap(qra[0], qr1[i], qr2[i])
qc.h(qra[0])
qc.measure(qra[0], cr[0])
\end{minted}
\end{frame}

\begin{frame}[fragile]{SWAP-test on qiskit}
\begin{minted}{python}
qasm_sim = Aer.get_backend('qasm_simulator')
SHOTS = 1000
count = execute(qc, qasm_sim, shots=SHOTS).result.get_count()
p0 = count.get('0', 0)/SHOTS
p1 = count.get('1', 0)/SHOTS
inner_prod = sqrt(2*max(p0 - 0.5, 0))
\end{minted}
\end{frame}


\begin{frame}{K-nearest neighbor classificator with swap-test}
\begin{enumerate}
    \item<1-> Consider some unlabelled instance \(\tilde{x}\) and some training set \((x_1, y_1); ...; (x_n, y_n)\) where \(y_i \in \{\ell_1, ..., \ell_m\}\)
    \item<2-> Calculate the inner product between \(\tilde{x}\) and any \(x_i\) through the swap-test;
    \item<3-> Pick the \(k\) elements whose inner product is bigger and their corresponding labels, infer \(\tilde{y}\) to be the most occurring label.
\end{enumerate}
\end{frame}


\begin{frame}[fragile]{Your turn!}
Build the swap-test circuit.

Build a classificator for IRIS problem, then calculate its accuracy. \bigskip

\begin{minted}{python}
from qiskit.ml.datasets import iris
sample_train, training_input, test_input, class_labels = 
    iris(training_size=40, test_size=10, n=4)
# len(training_input[key]) == 40 for key in ['A', 'B', 'C']
# len(test_input[key]) == 10 for key in ['A', 'B', 'C']

# fix qiskit.ml.datasets.iris code line 30: 
# test_size=test_size*len(class_labels)
\end{minted}
\end{frame}


\begin{frame}[fragile]{Your turn! (hint)}

\begin{minted}{python}
from heapq import nlargest
from operator import itemgetter
def most_common(lst): return max(set(lst), key=lst.count)

def quantum_classifier(x, training_set):
    k=3
    similarities = []
    for label in ['A', 'B', 'C']:
        for item in training_set[label]:
            the_ip = quantum_inner_product(x, item)
            similarities.append((the_ip, label))
    k_similarities = nlargest(k, similarities, key=itemgetter(0))
    _, k_labels = zip(*k_similarities)
    return most_common(k_labels)
\end{minted}
\end{frame}


\begin{frame}{More on swap-test classifier}

The Hadamard classifier (Schuld et al.) implements a whole classifier. 

\begin{center}
    \begin{quantikz}[]%
    \lstick{\(\ket{a}\)}\qw%
        & \gate{H}%
        & \ctrl{2}%
        & \gate{X}%
        & \ctrl{2}%
        & \qw%
        & \ctrl{2}%
        & \gate{H}%
        & \meter{discard 1} \\%
    \lstick{\(\ket{m}\)}\qw%
        & \gate{H}%
        & \qw%
        & \qw%
        & \ctrl{1}%
        & \gate{X}%
        & \ctrl{1} %
        & \ctrl{2}%
        & \qw\\%
    \lstick{\(\ket{d}\)}\qw%
        & \qw%
        & \gate{\tilde{x}}%
        & \qw%
        & \gate{x_1}%
        & \qw%
        & \gate{x_2}%
        & \qw%
        & \qw\\%
    \lstick{\(\ket{c}\)}\qw%
        & \qw%
        & \qw%
        & \qw%
        & \qw%
        & \qw%
        & \qw%
        & \targ{}%
        & \meter{}%
\end{quantikz}
\end{center}

\[p(\text{measure }\ket{c}\;0) = \begin{cases}
    <0.5, & d(\tilde{x}, x_1) < d(\tilde{x}, x_2) \\
    >0.5, & d(\tilde{x}, x_1) > d(\tilde{x}, x_2)
\end{cases} \]

\end{frame}

\begin{frame}[fragile]{Controlled-initialize}
\begin{minted}{python}
init_data = QuantumCircuit(n)
init_data.initialize(psi, range(n))
init_data_wo_reset = init_data.gates_to_uncompute().inverse()
control_init_data = init_data.control(1)

qc = ...
qc.append(control_init_data, ...)
\end{minted}
\end{frame}

\begin{frame}[fragile]{Your turn!}
Build the Hadamard classifier circuit. Use it to solve the IRIS problem. \bigskip

\end{frame}